The MacLeish Package: R Package for analyzing weather and spatial data

### 2022-06-06 joss_paper/paper.Rmd
added map but not working

@@

```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
knitr::include_graphics("phenocam.jpeg")
```

>>>>

```{r, eval=FALSE}
# why doesn't this work?
map
```

@@

```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
knitr::include_graphics(here::here("joss_paper", "phenocam.jpeg"))
```
